Estimating the Effect of Eviction on Assessment Values

### 2022-12-23 writing/presentations/december_7.tex
Updates from Overleaf

\institute[]{Department of Earth, Environmental, and Planetary Sciences  \\Brown University}

\author[Arjun Shanmugam]{}

@@

\begin{frame}{Data}
\begin{table}[H]
    \centering
    \tiny
    \input{output/01_exploratory/tables/summary_statistics.tex}
    \caption{Caption}
    \label{tab:my_label}
\end{table}
\end{frame}

\input{output/01_exploratory/tables/balance_table.tex}

\section{Empirical Strategy}

\begin{frame} [allowframebreaks]\frametitle{References}

        \bibliographystyle{apalike}
        \bibliography{bibfile}
\end{frame}

>>>>

\author[Arjun Shanmugam]{}
\setbeamertemplate{navigation symbols}{}

@@

\begin{frame}{Data}
\begin{table}[H]
    \centering
    \tiny
    \input{output/01_exploratory/tables/summary_statistics.tex}
    \label{tab:my_label}
\end{table}
\end{frame}

\begin{frame}{Data}
\begin{table}[H]
    \centering
    \tiny
    \input{output/01_exploratory/tables/balance_table.tex}
    \label{tab:my_label}
\end{table}
\end{frame}

\section{Empirical Strategy}
\begin{frame}{Empirical Strategy}
    \begin{enumerate}
        \item Most eviction cases in Massachusetts are filed in the Massachusetts Housing Court
        \item Within the Housing Court, cases are assigned to about 15 judges quasi-randomly conditional on city and time
        \item This is the basis for an examiner design study, which uses judge dummies as instruments
    \end{enumerate}
\end{frame}

\begin{frame}{Empirical Strategy}
\begin{table}[H]
    \centering
    \tiny
    \input{output/01_exploratory/tables/placebo_first_stage.tex}
    \label{tab:my_label}
\end{table}    
\end{frame}

\begin{frame}{Preliminary Results}
    \begin{table}[H]
        \centering
        \tiny
        \input{output/01_exploratory/tables/ln_total_val_results_table.tex}
        \label{tab:my_label}
    \end{table}
\end{frame}
\begin{frame}{Preliminary Results}
    \begin{table}[H]
        \centering
        \tiny
        \input{output/01_exploratory/tables/ln_bldg_val_results_table.tex}
        \label{tab:my_label}
    \end{table}
\end{frame}

\begin{frame}{Next Steps}
    \begin{enumerate}
        \item Figure out what to do about my lack of power
        \item Find a systematic way to drop observations in sparse city-years
        \item Speak to an assessor from Massachusetts to understand whether there is even a mechanism through which I might see an effect
        \item Think about whether my instrument is truly valid
    \end{enumerate}
\end{frame}
